caDDS: Community Assisted Distributed Database for Sequences

### 2020-06-19 Paper2020ACM/Paper2020.tex
Fixed grammar for presentation and cleaned up abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
300 words
- purpose and problems:
    - design a framework
    - design a database
- basic design:
- system summary:
    - master node and data node
- conclusion:
    - time complexity wise: 
    - proposed system has this pros
    - based system has this pros

working draft (insert kulang when info is ready):
 Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
working draft (insert kulang when info is ready):
 Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{abstract}

### 2020-06-19 Paper2020ACM/Presentation.tex
Fixed grammar for presentation and cleaned up abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO + RRL %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Abstract}
  Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{frame}
\section{Introduction}
\subsection{Genomic Concepts}
\begin{frame}{Genes}
  \begin{itemize}   
    \item all organisms have genes
    \item genes from DNA: AGCT
    \item genes are instructions and blueprints for life
\end{itemize}
\end{frame}

\begin{frame}{Genomics}
  \begin{block} {\textbf{Definition of Genomics}}
    Genomics is the study of all of a person's genes (the genome), including interactions of those genes with each other and with the person's environment. \cite{genomics-definition}
  \end{block}
  \begin{itemize}   
    \item study of genes
    \item more complex organisms have more complex genes
    \item studying complex organisms needs a lot of storage
  \end{itemize}
\end{frame}

\begin{frame}{Sequencing}
  \begin{itemize}   
    \item reading genes from cells is sequencing
    \item replications(coverage) \& fragmentation of DNA to read
    \item store the many fragments
  \end{itemize}
\end{frame}

\begin{frame}{Human Genome Project}
  \begin{itemize}   
    \item finished in 2003, project wanted to read the entire human genome
    \item didn't have the tools at the time
    \item big cost, many institutions, 10 years
  \end{itemize}
\end{frame}

@@

\subsection{System Summay}
\begin{frame}{System}
  \begin{itemize}   
    \item system is this
    \item distributed
    \item community assisted
  \end{itemize}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO + RRL %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Abstract}
  Genomic data the past few years have grown exponentially with the technology barely keeping up. The problem faced by genome researchers is the large data set and difficulty transferring the files. Previous distributed databases are either not meant for genomic data, or difficult to replicate. This paper lays the groundwork for a distributed database that is designed to easily scale to accommodate bigger storage, and also reduces the data speed bottleneck faced by centralized databases. The proposed system has a master node and data nodes. Data nodes should theoretically increase data transfer speeds even as the number of users increase. (to be updated based on conclusion) While current databases(e.g. NCBI) have more data, more users, and a live platform. The proposed system is aimed towards a smaller community, with more frequent and localized data, which the data storage can easily be expanded as the need arises. A recommendation is to implement the system and make the code public for the use of other communities.
\end{frame}
\section{Introduction}
\subsection{Genomic Concepts}
\begin{frame}{Genes}
  \begin{itemize}   
    \item all organisms have genes
    \item Genes are made of a certain molecular structure called DNA which correspond to information denoted by: A,G,C,T
    \item genes are instructions and blueprints for life
\end{itemize}
\end{frame}

\begin{frame}{Human Genes}
  \begin{itemize}   
    \item There is a lot of information in one human cell
    \item One human cell's entire genes laid out is 2 meters in length \cite{ency_sci_tech} and has $3.2x10^9$ base pairs \cite{introgenomics}
    \item Human body has a lot of information, that when laid out spans the earth to the moon six thousand times
\end{itemize}
\end{frame}

\begin{frame}{Genomics}
  \begin{block} {\textbf{Definition of Genomics}}
    Genomics is the study of all of a person's genes (the genome), including interactions of those genes with each other and with the person's environment. \cite{genomics-definition}
  \end{block}
  \begin{itemize}   
    \item \textbf{Genomics}: study of whole sets of genes and their interactions \cite{campbell}
    \item More complex organisms have more complex genes (many parts and interactions)
    \item Studying these complex organisms needs a lot of storage
    \item The current online portal mainly used to study this is NCBI \cite{campbell}
  \end{itemize}
\end{frame}

\begin{frame}{Sequencing}
  \begin{itemize}   
    \item Reading genes from cells is sequencing
    \item Replications (coverage) \& Fragmentation of DNA is necessary to read
    \item Every read stores the many fragments
    \item Each sequence read is redundant and uses a lot of space
  \end{itemize}
\end{frame}

\begin{frame}{Human Genome Project Successes}
  \begin{itemize}   
    \item 2 years after, the project led to a whole genome project for chimpanzees (human's closest relative) \cite{campbell}
    \item These led to many whole genome analysis of organisms (around 4,300 in 2013) \cite{campbell}
    \item Growing amount of research and data from genome research.
  \end{itemize}
\end{frame}

\begin{frame}{Human Genome Project}
  \begin{itemize}   
    \item Finished in 2003, project wanted to read the entire human genome
    \item Didn't have the mature tools at the time
    \item Big cost, many institutions, 10 years
  \end{itemize}
\end{frame}

@@

\subsection{System Summary}
\begin{frame}{System}
  \begin{itemize}   
    \item system is this
    \item distributed
    \item community assisted
  \end{itemize}
\end{frame}
